---
fontsize: 12pt
geometry: margin=1in
link-citations: yes
csl: ecology.csl
bibliography: library.bib
crossref:
  fig-title: Fig.
  fig-prefix: Fig.
  eq-prefix: Eq.
always_allow_html: true
tbl-cap-location: bottom
format:
  pdf:
    toc: false
    keep-tex: true
    latex-clean: false
    pdf-engine: pdflatex
    include-in-header:
      text: |
        \usepackage{xr}
        \externaldocument{si}
        \usepackage[default]{sourcesanspro}
        \usepackage{sourcecodepro}
        \usepackage{lineno}
        \usepackage{fvextra}
        \linenumbers
        \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
  docx:
    toc: false
    number-sections: false
    highlight-style: github
    html-math-method: katex
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(here)
library(knitr)
library(kableExtra)
here::i_am("ms/manuscript.qmd")
source(here("R/functions.R"))
para <- read_csv(here("data/fit_summary_model.csv"))
```


**Title: Title of your manuscript**

$$ $$

First Author^1,2^,
Second Author^2^, and
Third Author^3^

$$ $$

^1^ First Affiliation

^2^ Second Affiliation

^3^ Third Affiliation


Your abstract.

# Introduction

This is a manuscript template for Quarto markdown that uses R packages `targets` [@Landau2021] and `stantargets`.
`R/functions.R` contains R codes that I often use.

# Examples

## Equations

A centered parameterization of the Eight Schools model (@eq-cp; @Gelman2013).

$$
\begin{aligned}
\mu &\sim N(0,5) \\
\tau &\sim HalfCauchy(0,5) \\
\theta_j &\sim N(\mu, \tau) \\
y_j &\sim N(\theta_j, \sigma_j)
\end{aligned}
$$ {#eq-cp}

You can group multiple lines of equations to a single equation label.

In a non-centered parameterization of the @eq-cp, we fit latent Gaussian variables instead of directly estimating $\theta_j$:

$$
\tilde{\theta}_j \sim N(0, 1)
$$ {#eq-latent}

$$
\theta_j = \mu + \tau \tilde{\theta}_j.
$$  {#eq-ncp}

You can label each line too.

The half-cauchy distribution in the @eq-cp can be further rewritten as following:

$$
\begin{aligned}
\tilde{\tau} \sim U(0, \pi / 2) \\
\tau = 5 tan(\tilde{\tau})
\end{aligned}
$$

You can also write equations without labels.

Source codes can be loaded and printed, which may be useful for supporting information.

```{stan, file=here::here('stan/model.stan'), echo=TRUE, eval=FALSE, output.var="hoge"}
```

## Tables

It's easier to use `kableExtra` than manually writing markdown tables.
Here is the R code chunk to produce @tbl-eight_schools.

```{r, echo = TRUE, eval=FALSE}
schools_data <- tibble(
  School = LETTERS[1:8],
  `Estimated treatment effect, $y_j$`  = c(28, 8, -3, 7, -1, 1, 18, 12),
  `Standard error of effect estimate, $\\sigma_j$` = c(15, 10, 16, 11, 9, 11, 10, 18))

schools_data |>
  kbl(booktabs = TRUE, escape = FALSE) |>
    kable_styling(latex_options = "striped")
```

## Figures

I currently prefer to use `![]()` to insert images (@fig-theta_tau; @fig-theta_intervals) rather than using R code chunks.
It's easy for cross-references and putting greek letters.
The path for @fig-theta_tau can be `figs/theta_tau_line.png` or `..figs/theta_tau_line.png` depending on where you are working.
When you run `make` (i.e., Makefile), the first one is the correct path.
When you use `render` in VSCode, the second one is correct.
Using `here::here` is useful to specify the path to figures.

## Cross-reference from different files

We can also do cross-reference from different files, which is useful to refer figures and tables in supporting information.

Fig. S`\ref{fig-hist}`.

The above command will render the following

Fig. S\ref{fig-hist}.

You need these in the YAML.

```
\usepackage{xr}
\externaldocument{si}
```

This only works on LaTeX.

## Parameterized text

The posterior median of treatment effect for school A ($\theta_1$) is
`` `r
get_post_para(para, "theta[1]", "q50")` ``
with the 95% credible interval of
[
`` ` r
get_post_para(para, "theta[1]", "q2.5")` ``
,
`` ` r
get_post_para(para, "theta[1]", "q97.5", digits = 1, nsmall = 1)` ``
].

The above text will be rendered as following:

The posterior median of treatment effect for school A ($\theta_1$) is
`r get_post_para(para, "theta[1]", "q50")`
with the 95% credible interval of
[
`r get_post_para(para, "theta[1]", "q2.5")`
,
`r get_post_para(para, "theta[1]", "q97.5", digits = 1, nsmall = 1)`
].


# References

<div id="refs"></div>

\newpage

# Tables

```{r, echo=FALSE, eval=FALSE}
#| label: tbl-iris
#| tbl-cap: "Iris Data"
library(knitr)
kable(head(iris), format = "latex", table.envir = "table", position = "h!")
```

```{r, echo=FALSE, eval=TRUE}
#| label: tbl-eight_schools
#| tbl-cap: "Observed effects of special preparation on SAT-V scores in eight randomized experiments"

schools_data <- tibble(
  School = LETTERS[1:8],
  `Estimated treatment effect, $y_j$`  = c(28, 8, -3, 7, -1, 1, 18, 12),
  `Standard error of effect estimate, $\\sigma_j$` = c(15, 10, 16, 11, 9, 11, 10, 18))

schools_data |>
  kbl(booktabs = TRUE, escape = FALSE, table.envir = "table", position = "h!") |>
    kable_styling(latex_options = "striped")
```

Estimates are based on separate analyses for the eight experiments [@Gelman2013].

> - I don't know how to add greek letters in the caption but at least I can put greek letters outside the caption (e.g., $\theta_j$).

> - There is a bug for table cross-reference [(Section titles appear after tables (PDF) #2264)
](https://github.com/quarto-dev/quarto-cli/discussions/2264#discussioncomment-3541972).

\newpage

# Figures

![
The famous plot from @Gelman2013.
Conditional posterior means of treatment effects, $E(\theta_j | \tau, y)$ is plotted against the between school standard deviation $\tau$.
The stan model was fitted using dynamic branches.
](`r here::here("figs/theta_tau_line.png")`){#fig-theta_tau}


\newpage

![
The posterior means, 50% and 90% credible intervals of treatment effects ($\theta_j$).
](`r here::here("figs/theta_intervals.png")`){#fig-theta_intervals}
